AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-03-03 article/tex/main.tex
#7 tackles reviews

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
We introduce AIR4Children, Artificial Intelligence for Children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and Robotics (AIR).
We present current challenges and opportunities for a child-centred approaches for AIR. 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, affordable and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
Similarly, we propose to follow the philosophy of Montessori education to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
Finally, we conclude with few anecdotal experiences of our work and mainly we pose the future work of putting in practice what is proposed here to measure the impact on AIR in children of different socio-economical background, developmental stages and learning abilities. 
\end{abstract}

@@

@@

\section{Conclusions and future work}
In this work, we coin the term AIR4Children as a project that aims to tackle aspects of inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create teaching materials with a more child-centre approach for AI and Robotics.
We also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational materials.  
Similarly, it has been presented the initial phases of AIR4Children that include piloting, implementing and refining workshops for children in the age range between 6 to 14 to be implemented in Xicohtzinco, a town from Tlaxcala, M\'exico.
We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills to think creatively, with curiosity and open-minded as well as to develop a sense of wonder and joy for learning.

As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and Robotics and to evaluate the impact on these fields to children and to the community.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
We introduce AIR4Children, Artificial Intelligence for Children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and Robotics (AIR).
We present current challenges and opportunities for a child-centred approaches for AIR. 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, affordable and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware based on our initial pilots and experiences.
Similarly, we propose to follow the philosophy of Montessori education to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition.
Finally, we conclude with the opportunities of our work and mainly we pose the future work of putting in practice what is proposed here to measure the potential impact on AIR in children of different socio-economical background, developmental stages and learning abilities. 
\end{abstract}

@@

\subsection{Initial pilots of AIR4Children}
In 2013, a custom-make robot of 50USD were build to teach robotics to one child in which the challenging were to teach complex concepts in a fun way without any curriculum nor teaching materials. 
Then, in 2014, we managed to build a new robot prototype that make use of voice commands for easy interaction with children (Figure \ref{fig:teaser}(a)). 
With such prototype, we engaged with four children of a age range between 9 to 11, who enjoyed the voice command interaction of trying to move the robot in five commands (move forward, move backward, move right, move left and stop) (top image of Figure \ref{fig:teaser}(c)).
Recently, during three months from October 2020, we managed to virtually pilot Otto robot to one child accompanied with his mother for the constructions and the teaching of basis of AIR (bottom image of Figure \ref{fig:teaser}(c)).
Such pilots help us to clarify and to distill the aims of AIR4Children as a way to go for another round of pilots which will include curriculums and teaching materials to help both children, instructors (and perhaps their parents as well).

@@

\section{Conclusions and future work}
In this work, we coin the term AIR4Children as a project that aims to tackle aspects of inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create teaching materials with a more child-centre approach for AI and Robotics.
We also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational materials.  
We added our previous experience of few pilots since 2013 as way to narrow down the aims of AIR4Children.
Similarly, it has been presented the initial phases of AIR4Children that include piloting, implementing and refining workshops for children in the age range between 6 to 14 (to be implemented in Xicohtzinco, a town from Tlaxcala, M\'exico).
We also touched on the creation of curriculums following the philosophy of Montessori education, a non-traditional educational approach to help young audiences to develop skills to think creatively, with curiosity and open-minded and to develop a sense of wonder and joy for learning.

As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and Robotics and to evaluate the impact on these fields to children, parents and their community.
